---
title: "Black Panther: Kendrick + Friends"
author: "Angela Li"
date: "February 9, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

So I've been wanting to try out Josiah Parry's geniusR package for a while, and I hadn't found a good occasion to use it.

Until today, when Kendrick Lamar released [his album](https://open.spotify.com/album/5sOSzueqgCiVpXNcpd6QpL) for the upcoming movie *Black Panther*. Apparently he was asked to only record a few songs for it, but he ended up producing the entire album. I'm for it.

In the spirit of the original inspiration for the geniusR package, the release of Kendrick Lamar's album **DAMN.**, here goes a try with *Black Panther*. 

```{r load, results='hide', message=FALSE, warning=FALSE}
# Load libraries
library(geniusR)
library(tidyverse)
library(tidytext)
```

Let's get some lyrics!

```{r lyrics}
bp_song <- genius_lyrics(artist = "Kendrick Lamar", song = "Black Panther")

bp_song %>% 
  mutate(line = row_number())
```

Time for a tracklist!

```{r eval = FALSE}
bp_tracks <- genius_tracklist(artist = "Kendrick Lamar", album = "Black Panther")
```

So putting `artist` = `"Kendrick Lamar"` and `album` = `"Black Panther"` doesn't actually work, because Kendrick worked with a few other folks on this album, including The Weeknd and SZA, to name a few stars.

To make this work, what we want to do is look up the album on Genius and basically take the URL without dashes. The only reason I know this is because I may have been the one to suggest this feature.

```{r}
(bp_tracks <- genius_tracklist(artist = "Kendrick Lamar The Weeknd And Sza", album = "Black Panther The Album Music From And Inspired By"))
```
Sweet.

This is sort of a pain to type, so I'll store the strings instead.

```{r}
kendrick <- "Kendrick Lamar The Weeknd And Sza"
bp <- "Black Panther The Album Music From And Inspired By"

(bp_tracks <- genius_tracklist(artist = kendrick, album = bp))
```


```{r, eval = FALSE}
(bp_album <- genius_album(artist = kendrick, album = bp, nested = FALSE))
```

**Why doesn't this work???**

Oh, it's because each of the tracks has different artists. Aah, my suggestion of using the URL only works if each of the songs on the album is by the same person.

I think what we need to do is use rvest to actually scrape URLs from the page, instead of hacking together a URL that works 95% of the time. 

Guess this doesn't work for compilations. Time to submit an issue.
